Locoweed Volatiles

### 2024-03-09 locoweed-report.qmd
update locoweed report images

<div class="gallery">
<img src="img/loco-plants/IMG_0064.HEIC" alt="Image 1" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_0820 2.HEIC" alt="Image 2" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1165.HEIC" alt="Image 3" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1177.HEIC" alt="Image 4" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1923.HEIC" alt="Image 5" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

>>>>

<div class="gallery">
<img src="img/loco-plants/IMG_0064.jpg" alt="Image 1" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_0820 2.jpg" alt="Image 2" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1165.jpg" alt="Image 3" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1177.jpg" alt="Image 4" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1923.jpg" alt="Image 5" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>
